Shift-sensitive Power Transformations for Transforming Data to Normality

### 2023-01-27 manuscript/manuscript.Rmd
Update manuscript.Rmd

---
title: "Shift-sensitive Power Transformations for Transforming Data to Normality"
author: "Alex Zwanenburg"
date: "2023-01-06"
output: 
  pdf_document:
    latex_engine: lualatex
bibliography: "refs.bib"
header-includes:
   - \usepackage{amsmath}
   - \DeclareMathOperator*{\argmax}{argmax}
   - \DeclareMathOperator{\sgn}{sgn}
---

@@

require(power.transform)
require(ggplot2)
require(data.table)
require(latex2exp)

@@

@@

```{r shifted-distributions, echo=FALSE, fig.cap=cap}
cap <- paste0(
  "Power transformations modified to be shift-sensitive produce transformation parameters that are invariant to location.")

compute_lambda <- function(mu, x, method, shift=FALSE, robust=FALSE){
  # Create transformer object.
  transformer <- suppressWarnings(
    power.transform::find_transformation_parameters(
      x = x + mu,
      method = method,
      robust = robust,
      shift = shift,
      lambda = NULL))

.create_lambda_shift_data <- function(x, shift_range){

  box_cox_shift_values <- sapply(
    shift_range,
    compute_lambda,
    x = x,
    method = "box_cox",
    shift = TRUE,
    robust = FALSE)

  box_cox_shift_robust_values <- sapply(
    shift_range,
    compute_lambda,
    x = x,
    method = "box_cox",
    shift = TRUE,
    robust = TRUE)

  yeo_johnson_shift_values <- sapply(
    shift_range,
    compute_lambda,
    x = x,
    method = "yeo_johnson",
    shift = TRUE,
    robust = FALSE)

  yeo_johnson_shift_robust_values <- sapply(
    shift_range,
    compute_lambda,
    x = x,
    method = "yeo_johnson",
    shift = TRUE,
    robust = TRUE)

  data <- data.table::data.table(
    "mu" = log10(c(shift_range, shift_range)),
    "lambda" = c(
      box_cox_values,
      box_cox_shift_values,
      box_cox_shift_robust_values,
      yeo_johnson_values,
      yeo_johnson_shift_values,
      yeo_johnson_shift_robust_values),
    "method" = factor(
      x=rep(
        c("Box-Cox", "Yeo-Johnson"),
        each = 3L * length(shift_range)),
      levels=c("Box-Cox", "Yeo-Johnson")),
    "version" = factor(
      x=rep(
        c("original", "shift-sensitive", "robust shift-sensitive"),
        each = length(shift_range),
        times = 2L),
      levels = c("original", "shift-sensitive", "robust shift-sensitive")))

  return(data)
}

.create_density_plot <- function(x, plot_theme){
  p <- ggplot2::ggplot(
    data = data.table::data.table("x"=x),
    mapping = ggplot2::aes(
      x = x))
  p <- p + plot_theme
  p <- p + ggplot2::geom_density()
  p <- p + ggplot2::theme(
    axis.title = ggplot2::element_blank(),
    axis.line = ggplot2::element_blank(),
    axis.ticks = ggplot2::element_blank(),
    axis.text = ggplot2::element_blank(),
    panel.grid = ggplot2::element_blank(),
    panel.border = ggplot2::element_blank())

@@

.create_lambda_shift_plot <- function(data, plot_theme, limits, expected=FALSE){

  annotation_settings <- get_annotation_settings(plot_theme)

  p <- ggplot2::ggplot(
    data = data,
    mapping = ggplot2::aes(
      x = mu,
      y = lambda,
      colour = method,
      shape = version))
  p <- p + plot_theme
  p <- p + ggplot2::geom_point()
  p <- p + ggplot2::geom_hline(
    yintercept = 1.0, 
    linetype="longdash", 
    colour="grey40")
  p <- p + ggplot2::scale_x_continuous(
    name = latex2exp::TeX("$d$"),
    labels = scales::math_format())
  p <- p + ggplot2::scale_y_continuous(
    name = latex2exp::TeX("$\\lambda$"),
    limits = limits)

  if(expected){
      p <- p + ggplot2::annotate(
    geom = "text",
    x = 6,
    y = 1,
    label = "expected",
    colour=annotation_settings$colour,
    family=annotation_settings$family,
    fontface=annotation_settings$face,
    size=annotation_settings$geom_text_size,
    vjust=-1.0,
    hjust=1.0)
  }

@@

# Normal distribution.
x <- stats::rnorm(10000L)
shift_range <- 10^seq(from=0, to=6, by=0.1)

# Right skewed data
x_right_skewed <- (x - min(x) + 1)^0.1
x_right_skewed <- (x_right_skewed - mean(x_right_skewed)) / sd(x_right_skewed)

# Left skewed data
x_left_skewed <- (x - min(x))^3
x_left_skewed <- (x_left_skewed - mean(x_left_skewed)) / sd(x_left_skewed)

#### Normal distribution -------------------------------------------------------

data_normal <- .create_lambda_shift_data(
  x = x,
  shift_range = shift_range)

# Density
p_dens_normal <- .create_density_plot(
  x=x,
  plot_theme=plot_theme)

# Box-Cox
p_bc_normal <- .create_lambda_shift_plot(
  data = data_normal[method == "Box-Cox"],
  plot_theme = plot_theme,
  limits = c(-3.6, 1.1))
p_bc_normal <- p_bc_normal + paletteer::scale_color_paletteer_d(
  palette = "ggthemes::Tableau_10",
  drop = FALSE,
  guide = "none")
p_bc_normal <- p_bc_normal + ggplot2::scale_shape_discrete(guide="none")

# Yeo-Johnson
p_yj_normal <- .create_lambda_shift_plot(
  data=data_normal[method == "Yeo-Johnson"],
  plot_theme = plot_theme,
  limits = c(-3.6, 1.1))
p_yj_normal <- p_yj_normal + paletteer::scale_color_paletteer_d(
  palette = "ggthemes::Tableau_10",
  drop = FALSE,
  guide = "none")
p_yj_normal <- p_yj_normal + ggplot2::theme(
  axis.title.y = ggplot2::element_blank(),
  axis.text.y = ggplot2::element_blank())

@@

data_right <- .create_lambda_shift_data(
  x = x_right_skewed,
  shift_range = shift_range)

# Density
p_dens_right <- .create_density_plot(
  x = x_right_skewed,
  plot_theme = plot_theme)

# Box-Cox
p_bc_right <- .create_lambda_shift_plot(
  data = data_right[method == "Box-Cox"],
  plot_theme = plot_theme,
  limits = c(1.0, 65))
p_bc_right <- p_bc_right + paletteer::scale_color_paletteer_d(
  palette = "ggthemes::Tableau_10",
  drop = FALSE,
  guide = "none")
p_bc_right <- p_bc_right + ggplot2::scale_shape_discrete(guide="none")

# Yeo-Johnson
p_yj_right <- .create_lambda_shift_plot(
  data = data_right[method == "Yeo-Johnson"],
  plot_theme = plot_theme,
  limits = c(1.0, 65))
p_yj_right <- p_yj_right + paletteer::scale_color_paletteer_d(
  palette = "ggthemes::Tableau_10",
  drop = FALSE)
p_yj_right <- p_yj_right + ggplot2::theme(
  axis.title.y=ggplot2::element_blank(),
  axis.text.y=ggplot2::element_blank())

@@

data_left <- .create_lambda_shift_data(
  x = x_left_skewed,
  shift_range = shift_range)

# Density
p_dens_left <- .create_density_plot(
  x = x_left_skewed,
  plot_theme = plot_theme)

# Box-Cox
p_bc_left <- .create_lambda_shift_plot(
  data = data_left[method == "Box-Cox"],
  plot_theme = plot_theme,
  limits = c(-10.5, 0.5))
p_bc_left <- p_bc_left + paletteer::scale_color_paletteer_d(
  palette = "ggthemes::Tableau_10",
  drop = FALSE,
  guide = "none")
p_bc_left <- p_bc_left + ggplot2::scale_shape_discrete(guide="none")

# Yeo-Johnson
p_yj_left <- .create_lambda_shift_plot(
  data = data_left[method == "Yeo-Johnson"],
  plot_theme = plot_theme,
  limits = c(-10.5, 0.5))
p_yj_left <- p_yj_left + paletteer::scale_color_paletteer_d(
  palette = "ggthemes::Tableau_10",
  drop = FALSE,
  guide = "none")
p_yj_left <- p_yj_left + ggplot2::theme(
  axis.title.y=ggplot2::element_blank(),
  axis.text.y=ggplot2::element_blank())

@@

data_normal[, "distribution":="normal"]
data_left[, "distribution":="left-skewed"]
data_right[, "distribution":="right-skewed"]

aggregate_data <- data.table::rbindlist(list(data_normal, data_left, data_right))[, list("mean_lambda"=mean(lambda), "sd_lambda"=stats::sd(lambda)), by=c("method", "version", "distribution")]

p <- egg::ggarrange(
  plots=list(
    p_dens_normal, p_bc_normal, p_yj_normal,
    p_dens_right, p_bc_right, p_yj_right,
    p_dens_left, p_bc_left, p_yj_left),
  ncol=3,
  draw=FALSE)
p
```

@@

@@

>>>>

---
title: "Shift-sensitive Power Transformations for Transforming Data to Normality"
author: "Alex Zwanenburg"
date: "2023-01-06"
output: 
  pdf_document:
    latex_engine: lualatex
bibliography: "refs.bib"
header-includes:
   - \usepackage{amsmath}
   - \usepackage{booktabs}
   - \DeclareMathOperator*{\argmax}{argmax}
   - \DeclareMathOperator{\sgn}{sgn}
---

@@

require(power.transform)
require(ggplot2)
require(data.table)
require(latex2exp)
require(coro)

@@

parse_mean_sd_latex <- function(mu, sigma, digits=2L){
  return(paste0(
    "$", round(mu, digits=digits), " \\pm ", round(sigma, digits=digits), "$"
  ))
}

@@

```{r shifted-distributions, echo=FALSE, warning=FALSE, message=FALSE, fig.cap=cap}
cap <- paste0(
  "Power transformations modified to be shift-sensitive produce transformation parameters are invariant to location.")

# Non-standard evaluation
d <- distribution <- method <- mean_lambda <- sd_lambda <- NULL

# Density plot.
.create_density_plot <- function(x, plot_theme){
  p <- ggplot2::ggplot(
    data = data.table::data.table("x"=x),
    mapping = ggplot2::aes(
      x = x))
  p <- p + plot_theme
  p <- p + ggplot2::geom_density()
  p <- p + ggplot2::theme(
    axis.title = ggplot2::element_blank(),
    axis.line = ggplot2::element_blank(),
    axis.ticks = ggplot2::element_blank(),
    axis.text = ggplot2::element_blank(),
    panel.grid = ggplot2::element_blank(),
    panel.border = ggplot2::element_blank(),
    plot.title=ggplot2::element_text(
      hjust=0.5,
      size=ggplot2::rel(1.0)))
  p <- p + ggplot2::xlim(c(-5, 5))

@@

# Lambda plot,
.create_lambda_shift_plot <- function(data, plot_theme, limits, guide=FALSE){

  p <- ggplot2::ggplot(
    data = data,
    mapping = ggplot2::aes(
      x = d,
      y = lambda,
      colour = method,
      shape = version))
  p <- p + plot_theme
  p <- p + ggplot2::geom_point()
  p <- p + ggplot2::scale_x_continuous(
    name = latex2exp::TeX("$d$"),
    labels = scales::math_format())
  p <- p + ggplot2::scale_y_continuous(
    name = latex2exp::TeX("$\\lambda$"),
    limits = limits)

  if(guide){
     p <- p + paletteer::scale_color_paletteer_d(
      palette = "ggthemes::Tableau_10",
      drop = FALSE)

  } else {
    p <- p + paletteer::scale_color_paletteer_d(
      palette = "ggthemes::Tableau_10",
      drop = FALSE,
      guide = "none")
    p <- p + ggplot2::scale_shape_discrete(guide="none")
  }

@@

# Generator for creating parameters and data for all experiments.
generate_experiment_data <- coro::generator(
  function(
    x_normal,
    x_right_skewed,
    x_left_skewed){

    shift_range <- 10^seq(from=0, to=6, by=0.1)

    for(d in shift_range){
      for(distribution in c("normal", "right-skewed", "left-skewed")){
        if(distribution == "normal"){
          x <- x_normal

        } else if(distribution == "right-skewed"){
          x <- x_right_skewed

        } else if(distribution == "left-skewed"){
          x <- x_left_skewed
        }

        for(method in c("box_cox", "yeo_johnson")){
          for(shift in c(FALSE, TRUE)){
            for(robust in c(FALSE, TRUE)){
              # Skip if robust, but not shifted.
              if(robust && !shift) next

              if(!shift && !robust){
                version <- "original"

              } else if(!robust){
                version <- "shift-sensitive"

              } else {
                version <- "robust shift-sensitive"
              }

              yield(list(
                "x" = x + d,
                "d" = d,
                "distribution" = distribution,
                "method" = method,
                "shift" = shift,
                "robust" = robust,
                "version" = version
              ))
            }
          }
        }
      }
    }
  })

.compute_lambda <- function(parameter_set){
  # Create transformer object.
  transformer <- suppressWarnings(
    power.transform::find_transformation_parameters(
      x = parameter_set$x,
      method = parameter_set$method,
      robust = parameter_set$robust,
      shift = parameter_set$shift,
      lambda = NULL))

  return(
    data.table::data.table(
      "distribution" = parameter_set$distribution,
      "method" = parameter_set$method,
      "version" = parameter_set$version,
      "d" = log10(parameter_set$d),
      "lambda" = transformer@lambda
    ))
}

#### Computations --------------------------------------------------------------

# Normal distribution.
x_normal <- stats::rnorm(10000L)

# Right skewed data
x_right_skewed <- (x_normal - min(x_normal) + 1)^0.1
x_right_skewed <- (x_right_skewed - mean(x_right_skewed)) / sd(x_right_skewed)

# Left skewed data
x_left_skewed <- (x_normal - min(x_normal))^3
x_left_skewed <- (x_left_skewed - mean(x_left_skewed)) / sd(x_left_skewed)

# Generate all experiments.
experiments <- coro::collect(generate_experiment_data(
  x_normal = x_normal,
  x_right_skewed = x_right_skewed,
  x_left_skewed = x_left_skewed
))

# Start cluster
cl <- parallel::makeCluster(16L)

# Compute all data in parallel.
data <- parallel::parLapply(
  cl=cl,
  X=experiments,
  fun=.compute_lambda
)

# Stop cluster.
parallel::stopCluster(cl)

# Combine data into a single table.
data <- data.table::rbindlist(data)

# Update distribution, method and version to factors.
data$distribution <- factor(
  x = data$distribution,
  levels = c("normal", "right-skewed", "left-skewed"))
data$method <- factor(
  x = data$method,
  levels = c("box_cox", "yeo_johnson"),
  labels = c("Box-Cox", "Yeo-Johnson"))
data$version <- factor(
  x = data$version,
  levels = c("original", "shift-sensitive", "robust shift-sensitive"))

#### Normal distribution -------------------------------------------------------
# Density
p_dens_normal <- .create_density_plot(
  x=x_normal,
  plot_theme=plot_theme)
p_dens_normal <- p_dens_normal + ggplot2::ggtitle(label="normal distribution")

# Box-Cox
p_bc_normal <- .create_lambda_shift_plot(
  data = data[distribution == "normal" & method == "Box-Cox"],
  plot_theme = plot_theme,
  limits = c(-3.6, 1.1))

# Yeo-Johnson
p_yj_normal <- .create_lambda_shift_plot(
  data=data[distribution == "normal" & method == "Yeo-Johnson"],
  plot_theme = plot_theme,
  limits = c(-3.6, 1.1))

@@

# Density
p_dens_right <- .create_density_plot(
  x = x_right_skewed,
  plot_theme = plot_theme)
p_dens_right <- p_dens_right + ggplot2::ggtitle(label="right-skewed distribution")

# Box-Cox
p_bc_right <- .create_lambda_shift_plot(
  data =data[distribution == "right-skewed" & method == "Box-Cox"],
  plot_theme = plot_theme,
  limits = c(1.0, 65))

# Yeo-Johnson
p_yj_right <- .create_lambda_shift_plot(
  data = data[distribution == "right-skewed" & method == "Yeo-Johnson"],
  plot_theme = plot_theme,
  limits = c(1.0, 65))

@@

# Density
p_dens_left <- .create_density_plot(
  x = x_left_skewed,
  plot_theme = plot_theme)
p_dens_left <- p_dens_left + ggplot2::ggtitle(label="left-skewed distribution")

# Box-Cox
p_bc_left <- .create_lambda_shift_plot(
  data = data[distribution == "left-skewed" & method == "Box-Cox"],
  plot_theme = plot_theme,
  limits = c(-10.5, 0.5),
  guide = TRUE)

# Yeo-Johnson
p_yj_left <- .create_lambda_shift_plot(
  data = data[distribution == "left-skewed" & method == "Yeo-Johnson"],
  plot_theme = plot_theme,
  limits = c(-10.5, 0.5))

@@

aggregate_data <- data[, list("mean_lambda"=mean(lambda), "sd_lambda"=stats::sd(lambda)), by=c("method", "version", "distribution")]
aggregate_data$distribution <- factor(
  x=aggregate_data$distribution,
  levels = c("normal", "left-skewed", "right-skewed"))
aggregate_data[, "text":=parse_mean_sd_latex(mu=mean_lambda, sigma=sd_lambda)]

p <- egg::ggarrange(
  plots=list(
    p_dens_normal, p_bc_normal, p_yj_normal,
    p_dens_right, p_bc_right, p_yj_right,
    p_dens_left, p_bc_left, p_yj_left),
  ncol=3,
  heights=c(0.5, 1.0, 1.0),
  byrow=FALSE,
  draw=FALSE)
p
```

@@

```{r, echo=FALSE, results="asis"}
table_data <- data.table::dcast(
  aggregate_data,
  distribution ~ version + method,
  value.var = "text",
  sep = " ")

knitr::kable(
  table_data,
  caption = "Estimates and deviation of transformation parameter $\\lambda$ under location shifts",
  label = "shifted-distributions-table",
  format = "latex",
  escape = FALSE,
  booktabs = TRUE)
```

@@

```{r}
# Generator for creating parameters and data for all experiments.
generate_experiment_data <- coro::generator(
  function(
    x_normal,
    x_right_skewed,
    x_left_skewed){

    n <- 20
    k_range <- (seq_len(n) - 1)^2 /((n-1)^2 * 5)  
    # k_range <- c(0.0, 0.001, 0.002, 0.005, 0.010, 0.020, 0.050, 0.100, 0.200)

    for(distribution in c("normal", "right-skewed", "left-skewed")){
      if(distribution == "normal"){
        x <- x_normal

      } else if(distribution == "right-skewed"){
        x <- x_right_skewed

      } else if(distribution == "left-skewed"){
        x <- x_left_skewed
      }
      for(ii in seq_len(20)){
        for(k in k_range){
          # Compute interquartile range.
          interquartile_range <- stats::IQR(x)

          # Compute upper and lower quartiles.
          q_lower <- stats::quantile(x, probs=0.25, names=FALSE)
          q_upper <- stats::quantile(x, probs=0.75, names=FALSE)

          # Set data where the outliers will be copied into.
          x_outlier <- x

          if(k != 0.0){
            n_draw <- ceiling(k * 0.5 * length(x))

            # Generate outlier values that are smaller than Q1 - 1.5 IQR or larger
            # than Q3 + 1.5 IQR.
            outlier <- c(
              q_lower - 1.5 * interquartile_range - 3.0 * stats::runif(n_draw),
              q_upper + 1.5 * interquartile_range + 3.0 * stats::runif(n_draw))

            # Randomly insert outlier values.
            x_outlier[sample(seq_along(x), size=2*n_draw, replace=FALSE)] <- outlier
          }

          #for(method in c("box_cox", "yeo_johnson")){
          for(method in c("yeo_johnson")){
            for(weight_method in c("none", "tukey_window", "tapered_step_window")){
            # for(weight_method in c("none", "tukey_window", "step_window", "tapered_step_window", "trim_transformation", "trim_residual", "tukey_biweight_transformation", "tukey_biweight_residual", "huber_weight_transformed", "huber_weight_residual")){

              weight_method_name <- weight_method

              for(tukey_window_k in c(0.80, 0.60, 0.40, 0.20, 0.00)){
                if(weight_method == "none" && tukey_window_k != 0.00) next

                yield(list(
                  "ii" = ii,
                  "x" = x_outlier,
                  "k" = k,
                  "distribution" = distribution,
                  "method" = method,
                  "robust" = weight_method != "none",
                  "weight_method" = weight_method,
                  "weight_method_name" = paste0(weight_method_name, "_k_", tukey_window_k),
                  "tukey_window_k" = tukey_window_k
                ))
              }

              # if(weight_method == "tukey_window"){
              #   for(tukey_window_k in c(0.9, 0.8, 0.7, 0.6, 0.5)){
              #     yield(list(
              #       "x" = x_outlier,
              #       "k" = k,
              #       "distribution" = distribution,
              #       "method" = method,
              #       "robust" = weight_method != "none",
              #       "weight_method" = weight_method,
              #       "weight_method_name" = paste0(weight_method_name, "_k_", tukey_window_k),
              #       "tukey_window_k" = tukey_window_k
              #     ))
              #   }
              # } else {
              #   yield(list(
              #     "x" = x_outlier,
              #     "k" = k,
              #     "distribution" = distribution,
              #     "method" = method,
              #     "robust" = weight_method != "none",
              #     "weight_method" = weight_method,
              #     "weight_method_name" = weight_method_name
              #   ))
              # }
            }
          }
        }
      }
    }
  })

.compute_lambda <- function(parameter_set){
  # Create transformer object.
  transformer <- suppressWarnings(
    power.transform::find_transformation_parameters(
      x = parameter_set$x,
      method = parameter_set$method,
      robust = parameter_set$robust,
      shift = TRUE,
      weight_method = parameter_set$weight_method,
      k = parameter_set$tukey_window_k,
      lambda = NULL))

  return(
    data.table::data.table(
      "distribution" = parameter_set$distribution,
      "method" = parameter_set$method,
      "weight_method" = parameter_set$weight_method,
      "weight_method_name" = parameter_set$weight_method_name,
      "k" = parameter_set$k,
      "lambda" = transformer@lambda,
      "kappa" = parameter_set$tukey_window_k,
      "ii" = parameter_set$ii
    ))
}

# Normal distribution.
x_normal <- stats::rnorm(10000L)

# Right skewed data
x_right_skewed <- (x_normal - min(x_normal) + 1)^0.1
x_right_skewed <- (x_right_skewed - mean(x_right_skewed)) / sd(x_right_skewed)

# Left skewed data
x_left_skewed <- (x_normal - min(x_normal))^3
x_left_skewed <- (x_left_skewed - mean(x_left_skewed)) / sd(x_left_skewed)

# Generate all experiments.
experiments <- coro::collect(generate_experiment_data(
  x_normal = x_normal,
  x_right_skewed = x_right_skewed,
  x_left_skewed = x_left_skewed
))

# Start cluster
cl <- parallel::makeCluster(16L)

# Compute all data in parallel.
data <- parallel::parLapply(
  cl=cl,
  X=experiments,
  fun=.compute_lambda
)

# Stop cluster.
parallel::stopCluster(cl)

# Combine data into a single table.
data <- data.table::rbindlist(data)

# Update distribution, method and version to factors.
data$distribution <- factor(
  x = data$distribution,
  levels = c("normal", "right-skewed", "left-skewed"))
data$method <- factor(
  x = data$method,
  levels = c("box_cox", "yeo_johnson"),
  labels = c("Box-Cox", "Yeo-Johnson"))
data$kappa <- factor(data$kappa)

# Find target lambda values in the absence of any outliers.
target_data <- data[weight_method=="none" & k == 0.0, mget(c("distribution", "ii", "lambda", "method"))]
data.table::setnames(target_data, old="lambda", new="target_lambda")

# Merge target lambda values into the main data.
data <- data[target_data, on=.NATURAL]

# Compute difference with target lambda.
data[, "diff_lambda":=lambda - target_lambda]

summary_data[, list(deviation=sum(abs(diff_lambda))), by=c("distribution", "weight_method_name")][order(distribution, deviation)]

# Compute average.
new_data <- data[, list(lambda = mean(lambda)), by=c("k", "kappa", "weight_method", "distribution")]

p <- ggplot2::ggplot(
  data = new_data[distribution=="left-skewed"],
  mapping = ggplot2::aes(
    x = k,
    y = lambda,
    colour = kappa,
    linetype = weight_method))
p <- p + plot_theme
# p <- p + ggplot2::geom_point()
p <- p + ggplot2::geom_line()
p <- p + ggplot2::scale_x_continuous(
  name = latex2exp::TeX("$k$"),
  trans = "sqrt")
p <- p + ggplot2::scale_y_continuous(
  name = latex2exp::TeX("$\\lambda$"))
